Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-05-27 paper.tex
table error fixed
abstract redefined

%%% Put your own title + short title here:
\title{Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s}$ =13 TeV}
\ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers

@@

To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV. The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016 because of increased statistics for high-multiplicity pp collisions.  The results are compared to previous measurements by other LHC experiments. In addition, we explore possible physical origins of the ridge effects in small systems by studying the results as a function of the energy scale of the hard fragmentation process and comparing the various theoretical models tuned for the initial and final state effect.
\end{abstract}

@@

%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
%\bibliographystyle{utphys}   % Remember we use title in the biblio
%\bibliography{biblio}
%\input {bibliography.tex}

%%%%%%%%% appendix with author list
\newpage
\appendix
%
%\input{}               %%%%%%%%%%% put your appendices here
%

%\section{The ALICE Collaboration}
%\label{app:collab}
%\input{authorlist-preprint.tex}  %%%%%%% done by webmaster team

>>>>

%%% Put your own title + short title here:
\title{Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
\ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers

@@

To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV with ALICE. The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016. Jet events are selected by two methods. The first one is done by seeing the transverse momentum of  leading particle in the pseudorapidity range $|\eta|<0.9$. The second method is done by reconstruction of charged jets using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. The measured ridge yield is consistent with the previous results from other LHC experiments. Furthermore, the ridge yield is found to be independent of the energy scale of the hard scattering process. This observation can help identify the origins of the ridge in small systems.

\end{abstract}

@@

\newpage
\appendix
